\documentclass[10pt]{article}
\title{CS311 Assignment 2}
\author{Emily Dunham}
\date{7/10/2013}
\def\name{Emily Dunham}

\begin{document}

\maketitle

\section{a design for your system, as well as places your implementation deviated from this design}

My initial design was to follow the outline for the code given in the
assignment description. My implementation deviated in that it did not work.

\section{a work log, detailing what you did when}

For the first 9 days during which the assignment was available, I assumed that
my code from last time I took the class would work. 

Today, I evaluated that code and realized that it did not in fact work. I then
re-watched the relevant video lectures, re-read the applicable sections of the
textbook, and was still unable to get my code working. I considered contacting
Kevin to ask for help but realized that he would probably mock me in front of
the whole class if I attempted to solve the assignment this close to its due
date, and decided that it'd be less traumatic to accept a reduced grade than
to be publicly taunted about my incompetence at time management. 

\section{any challenges you overcame in completing this assignment}

I had various challenges, as mentioned above, but did not successfully
overcome them.

\section{what do you think the main point of this assignment is?}

The point is nominally to teach us to read man pages and to get us back into
the patterns of writing, testing, and debugging C code. 

\section{how did you ensure your solution was correct?}

I did not ensure that my solution was correct, because I did not complete a
working solution.

\section{what did you learn?}

I learned that I was bad at this stuff last year, I am still bad at it now,
and I should probably start considering alternate career paths if I want to
graduate while Kevin's teaching at OSU.

\end{document}
